---
title: "Inferential Statistics"
author: ""
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE
)
```

```{r, results='hide', warning=FALSE, message=FALSE, attr.source='.numberLines'}
library(ggplot2)
library(readxl)
library(tidyverse)
```

```{r, results='hide', warning=FALSE, message=FALSE, attr.source='.numberLines'}
df <- read_xlsx(
    path = "17-Influence of Webinars and Seminars on Students’ Academic Performance.xlsx"
)
```

------------------------------------------------------------------------

### **Hypotheses:**

-   **Null Hypothesis (H0):** The mean perceptions of the impact of webinar and seminar attendance on academic performance are the same among participants.

-   **Alternative Hypothesis (H1):** There is a significant difference in the mean perceptions of the impact of webinar and seminar attendance on academic performance among participants.

> Type of T-Test: This scenario corresponds to an Independent Two-Sample T-Test.

```{r, results='hide', warning=FALSE, message=FALSE, attr.source='.numberLines'}
graduates <- df[
    df$`What is your current level of education?`
    %in%
    c(
        "Undergraduate (Bachelor's degree)",
        "Graduate (Master's or higher)"
    ),
]

graduates$Attendance <- as.numeric(
    factor(
        x = graduates$`Do you attend webinars and seminars related to your study?`,
        levels = c(
            "Strongly Disagree",
            "Disagree",
            "Neutral",
            "Agree",
            "Strongly Agree"
        )
    )
)

t_test_result <- t.test(
    formula = Attendance ~ `What is your current level of education?`,
    var.eqaul = TRUE,
    data = graduates
)
```

### **Conclusion:**

-   **p-value (0.08349) \> 0.05:** This suggests that there is not enough evidence to reject the null hypothesis.

-   **Confidence Interval:** At 95% confidence interval, there is no significant difference in the mean perceptions of attendance between Graduate and Undergraduate participants.

------------------------------------------------------------------------

### **Hypotheses:**

-   **Null Hypothesis (H0):** The means of responses to the accessibility of webinars are equal across different educational levels.

-   **Alternative Hypothesis (H1):** At least one group mean of responses to the accessibility of webinars is different from the others.

> Type of ANOVA Test: This scenario corresponds to a one-way ANOVA.

```{r, results='hide', warning=FALSE, message=FALSE, attr.source='.numberLines'}
graduates <- df[
    df$`What is your current level of education?`
    %in%
    c(
        "High School",
        "Undergraduate (Bachelor's degree)",
        "Graduate (Master's or higher)",
        "Others (please specify)"
    ),
]


graduates$Accessibility <- as.numeric(
    factor(
        x = graduates$`Preferences [Webinars are more accessible to a wider audience compared to seminars.]`,
        levels = c(
            "Strongly Disagree",
            "Disagree",
            "Neutral",
            "Agree",
            "Strongly Agree"
        )
    )
)

t_test_result <- aov(
    formula = Accessibility ~ `What is your current level of education?`,
    data = graduates,
)

summary(graduates)
```



## One Way Anova Test
One-way ANOVA: One-way When there is a single categorical independent variable (also known as a factor) and a single continuous dependent variable, an ANOVA is employed. It seeks to ascertain whether there are any notable variations in the dependent variable’s means across the levels of the independent variable.
 
Two-way ANOVA: When there are two categorical independent variables (factors) and one continuous dependent variable, two-way ANOVA is used as an extension of one-way ANOVA. You can evaluate both the direct impacts of each independent variable and how they interact with one another on the dependent variable.
-----------------------------------------


One-way ANOVA test is performed using mtcars dataset which comes preinstalled with dplyr package between disp attribute, a continuous attribute and gear attribute, a categorical attribute.here are some steps.

Setup Null Hypothesis and Alternate Hypothesis
H0 = mu = mu01 = mu02(There is no differencebetween average displacement for different gears)
H1 = Not all means are equal.

```{r}
mtcars_aov <- aov(mtcars$disp~factor(mtcars$gear))
summary(mtcars_aov)
```
Df: The model’s degrees of freedom.
Sum Sq: The sums of squares, which represent the variability that the model is able to account for.
Mean Sq: The variance explained by each component is represented by the mean squares.
F-value: It is the measure used to compare the mean squares both within and between groups.
Pr(>F): The F-statistics p-value, which denotes the factors’ statistical significance.
Residuals: Relative deviations from the group mean, are often known as residuals and their summary statistics.


## Performing two annova test
A two-way ANOVA test is performed using mtcars dataset which comes preinstalled with dplyr package between disp attribute, a continuous attribute and gear attribute, a categorical attribute, am attribute, a categorical attribute.

Setup Null Hypothesis and Alternate Hypothesis
H0 = mu0 = mu01 = mu02(There is no difference between average displacement for different gear)
H1 = Not all means are equal

```{r}
install.packages("dplyr")
 
# Loading the package
library(dplyr)
 
# Variance in mean within group and between group
histogram(mtcars$disp~mtcars$gear, subset = (mtcars$am == 0),
        xlab = "gear", ylab = "disp", main = "Automatic")
histogram(mtcars$disp~mtcars$gear, subset = (mtcars$am == 1),
        xlab = "gear", ylab = "disp", main = "Manual")


# anova test
mtcars_aov2 <- aov(mtcars$disp~factor(mtcars$gear) *
                            factor(mtcars$am))
summary(mtcars_aov2)

```

